
\begin{thebibliography}{00}
    \bibitem{adheetee} Syed Mohidul Islam, Most Fowziya Akther Houya, Syed Mynul Islam, Salekul Islam and Nahid Hossain, Adheetee: A Comprehensive Bangla Virtual Assistant, 2019.
    \bibitem{speech-recog-bengali} S.M. Saiful Islam Badhon, Md. Habibur Rahaman, Farea Rehnuma Rupon, State of art Research in Bengali Speech Recognition, 2020.
    \bibitem{whisper} Radford et al., Robust Speech Recognition via Large-Scale Weak Supervision, 2022.
    \bibitem{doly} Md. Kowsher, Farhana Sharmin Tithi, M Ashraful Alam, Mohammad Nurul Huda, Mir Md Moheuddin, Md. Golam Rosul, Doly: Bengali Chatbot for Bengali Education, 2019.
    \bibitem{bangla-bert} Bhattacharjee et al., BanglaBERT: Language Model Pretraining and Benchmarks for Low-Resource Language Understanding Evaluation in Bangla, 2022.
    \bibitem{tacotron} Shen et al., NATURAL TTS SYNTHESIS BY CONDITIONING WAVENET ON MEL SPECTROGRAM PREDICTIONS, 2018.
    \bibitem{LLaMA} Touvron et al., LLaMA: Open and Efﬁcient Foundation Language Models, 2023.
    \bibitem{siri-experience} Jerome R. Bellegarda, ``Large–Scale Personal Assistant Technology Deployment: the Siri Experience, 2013.
%    \bibitem{rl-chatbot} Elena Ricciardelli, Debmalya Biswas, Self-improving Chatbots based on Reinforcement Learning, 2019.
    \bibitem{chatbot} Shafquat Hussain, Omid Ameri Sianaki, Nedal Ababneh, A Survey on Conversational Agents/Chatbots Classification and Design Techniques, 2019.
    \bibitem{text-to-speech} Dosik Moon, Web-Based Text-to-Speech Technologies in Foreign Language Learning: Opportunities and Challenges, 2012.
    \bibitem{siri} AppleSiri, http://www.apple.com/ios/siri/, 011.
    \bibitem{google-mobile} Google Mobile, http://www.google.com/mobile/voice- actions, 2008.
    \bibitem{google-now} Google Now, http://www.google.com/landing/now, 2012.
    \bibitem{microsoft-tellme} Microsoft Tellme, http://www.microsoft.com/en-us/ Tellme/consumers/default.aspx, 2008.
    \bibitem{nuance-dragon} Nuance Dragon Go!, http://www.nuance.com/products/dragon-go-in-action/index.htm, 2011.
    \bibitem{nuance-nina} Nuance Nina, http://www.nuance.com/for-business/by- solution/customer-service-solutions/solutions-services/ mobile-customer-service/nina/index.htm, 2012.
    \bibitem{speaktoit} Speaktoit Assistant, http://www.speaktoit.com/index.htm, 2012.
    \bibitem{mostspoken} Chad Emery, "The 33 Most Spoken Languages in the World" Langoly https://www.asme.org/engineering-topics/articles/renewable-energy/catching-the-sun (accessed July 14, 2023).
    \bibitem{disabled-stats} Moyukh Mahtab, Faria Selim, "UNICEF concerned that more than half of children with disabilities in Bangladesh do not go to school" unicef Bangladesh https://www.unicef.org/bangladesh/en/press-releases/unicef-concerned-more-half-children-disabilities-bangladesh-do-not-go-school (accessed July 14, 2023).
    \bibitem{litaracy-bangladesh} Mir Mohammad Jasim, "Bangladesh’s slow march towards 100\% literacy" The Business Standard https://www.tbsnews.net/bangladesh/education/bangladeshs-slow-march-towards-100-literacy-492058 (accessed July 14, 2023).
    \bibitem{verbal-disabled-stats} Govt\. Bangladesh, "Report on National Survey on Persons with Disabilities (NSPD) 2021 (December 2022) [EN/BN]" reliefweb https://reliefweb.int/report/bangladesh/report-national-survey-persons-disabilities-nspd-2021-december-2022-enbn (accessed July 14, 2023).
    \bibitem{english-speaker-bangladesh} Pinon, Robert; Haydon, Jon (December 2010), The Benefits of the English Language for Individuals and Societies: Quantitative Indicators from Cameroon, Nigeria, Rwanda, Bangladesh and Pakistan, Euromonitor International Ltd
    \bibitem{bangla-tts} Sifat Hossain, https://github.com/shhossain/BanglaTTS, 2023.
    \bibitem{bangla-stt} Sifat Hossain, https://github.com/shhossain/BanglaSpeech2Text, 2023.
\end{thebibliography}
